Scale Space Edge Detection

### 2018-03-10 paper.tex
Fix block_all_edges label
Add edge selection subsection to implementation

@@

In contrast, our edge detection algorithm produces the following result:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_final.png}
  \caption{The final output of our program on the block image}
  \label{block_final}
\end{figure}
The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
Unfortunately, the edge of the shadow is not a continuous path.
This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
We can see this by displaying the full set of edges:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
  \caption{All edges of the block image as detected by our program}
  \label{block_final}
\end{figure}
In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.

>>>>

Then, to find all edges in the image, we simply run the marching cubes algorithm on every voxel in the image like so:
\begin{lstlisting}
function find_edges()
    voxel_visited = falses((x->x-1).(size(L)))
    edges = []
    p = Progress(prod(size(voxel_visited)), 1)
    @nloops 3 i voxel_visited begin
        edge = marching_cubes((@ntuple 3 i)..., voxel_visited)
        if length(edge) > 0
            push!(edges, edge)
        end
        next!(p)
    end
    return edges
end
\end{lstlisting}

\subsection{Selecting images by strength}

Now that we have found all scale space edges, it remains to select an ``interesting'' subset of them to display.
To do this, we rank the edges by their integrated edge strength as described in the Theory and take the first $n$ of them to be sufficiently important to display.
% TODO: fix this
\begin{lstlisting}
function edge_importance(edge)
    total = 0
    for (x, y, t) in edge
        total += sqrt(GL[x,y,t])
    end
    return total
end

function n_strongest_edges(edges, n)
    return sort(edges, by=edge_importance, rev=true)[1:n]
end
\end{lstlisting}

We then have a function to flatten the edge sets back into scale space by iterating though them and forming a boolean tensor if there is a edge inside that voxel.
\begin{lstlisting}
function flatten_edges(edges, L)
    edge_map = falses((x->x-1).(size(L)))
    for edge in edges
        for (x, y, t) in edge
            edge_map[x,y,t] = true
        end
    end
    return edge_map
end
\end{lstlisting}

Finally, we flatten the boolean tensor into an image by taking the logical disjunction of all values at a given spatial location in the image.
\begin{lstlisting}
function flatten_scale(Lp, func=any)
    return mapslices(func, Lp, 3)
end
\end{lstlisting}

@@

In contrast, our edge detection algorithm produces the following result:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_final.png}
  \caption{The final output of our program on the block image}
  \label{block_final}
\end{figure}
The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
Unfortunately, the edge of the shadow is not a continuous path.
This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
We can see this by displaying the full set of edges:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
  \caption{All edges of the block image as detected by our program}
  \label{block_all_edges}
\end{figure}
In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.
